%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Morgan Holland} % Your name
\address{601-572-7025 \\ morganbholland@gmail.com \\ 2750 Old Saint Augustine Rd. D33 Tallahassee, FL 32301} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Florida State University, COSSPP} \hfill {\em 2022 (expected)} \\ 
Doctorate of Philosophy in Economics \\

{\bf University of South Carolina, Moore School of Business} \hfill {\em 2015} \\
Master of Arts in Economics \\

{\bf Mississippi College, School of Business} \hfill {\em 2010}\\
Bachelor of Science in Business Administration

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Florida State University}{August 2015 - December 2020}{Research/Teaching Assistant}{Tallahassee, FL}
\item Proposed and developed economic research projects both individually and in collaboration with faculty.
\item Compiled and analyzed data from various sources to generate and investigate research hypotheses.
\item Developed mathematical models of economic phenomena.
\item Applied numerical methods to solve complex modelling problems.
\item Assisted faculty in developing course materials, class management, and grading.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Florida State University}{May 2017 - June 2021}{Instructor}{Tallahassee, FL}
\item Taught undergraduate level statistics and econometrics in person and online.
\item Integrated statistical software with course materials.
\item Developed custom instruction materials for statistics using economic data.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of South Carolina}{September 2013 - December 2013}{Research Assistant}{Columbia, SC}
\item Located and retrieved ownership data from Initial Public Offering (IPO) prospectuses.
\item Constructed custom spreadsheets of IPO data.
\item Performed literature searches for scholarly articles on several subjects related to corporate finance.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{South Carolina Office of Regulatory Staff}{July 2012 - September 2013}{Auditor}{Columbia, SC}
\item Advocated on behalf of the public in utility rate case proceedings before the South Carolina Public Service Commission.
\item Audited utility rate case filings to verify the accuracy of financial data.
\item Recommended adjustments to test-year revenue requirement analyses based on company financial data and rate case filings.
\item Crafted written testimony to be filed with the South Carolina Public Service Commission.
\item Reviewed nuclear plant construction invoices for compliance with the South Carolina Base Load Review Act and consistency with company financial documents.
\item Examined telecommunications company filings and financial documents for compliance with telecommunications law.

\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Mississippi Department of Finance and Administration}{January 2011-July 2012}{Accountant/Auditor}{Jackson, MS}
\item Pre-audited payments to State Treasurer for errors.
\item Assisted state agencies in completing payments to the State Treasury.
\item Approved transactions in a computerized accounting system.
\item Verified accuracy of daily deposits to the State Treasury.


\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Computer Proficiencies}

\begin{rSubsection}{Programming}{}{}{}
    \item {\em Expert}: R, Julia
    \item {\em Intermediate}: Matlab, Stata 
    \item {\em Beginner}: Python (Numpy, Pandas)
\end{rSubsection}

\begin{rSubsection}{Spreadsheet and Database}{}{}{}
    \item {\em Intermediate}: Excel 
    \item {\em Beginner}: SQL, MongoDB, JSON
\end{rSubsection}

\begin{rSubsection}{Document and Presentation Creation, Literate Programming}{}{}{}
    \item \LaTeX, Lyx, Rweave, Rmarkdown, Jupyter, Word, Powerpoint
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%	Academic Research
%----------------------------------------------------------------------------------------
\begin{rSection}{Academic Research}

\begin{rSubsection}{Working Papers}{}{}{}
\item {\em Growth, Income Distribution, and Political Economy Implications of Automation} (With Manoj Atolia and Jonathan Kreamer)
\item {\em The Option Value of Monitoring in Relationship Banking}
\end{rSubsection}

\begin{rSubsection}{Works in Progress}{}{}{}
\item {\em The Effect of the Americans with Disabilities Act on Earnings and Employment Outcomes for People with Disabilities: An Intersectional Approach}
\end{rSubsection}

\end{rSection}

%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
